Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

In our survey, we could not find an answer about the right moment for the
introduction of chatbot technologies. The response to questions regarding to
change of behavior during and after the first stay-at-home stage of the pandemic
do not suggest that a major (or minor, such as new higher education
laws\footnote{We seem to have one of these, at least in Spain, every 10 years or
  so.} or the introduction of new degrees) crisis could be an opportunity to
introduce new technologies. The reason being that it does not bring major
changes in attitude. Although changes driven by external forces do offer the
chance of piloting new technologies, they do not seem to bring internal changes
in educators' attitudes (which, after all, is bound to be the same). In absence
of a clear answer in this direction, the right moment to introduce new
technologies is always when the IT and managing staff is ready to support it
(since, as we have seen before, ``official'' support is one of the factors that
is most valued by teachers).

>>>>

In our survey, we could not find an answer about the right moment for the
introduction of chatbot technologies. The response to questions regarding the
change of behavior during and after the first stay-at-home stage of the pandemic
do not suggest that a major (or minor, such as new higher education
laws\footnote{We seem to have one of these, at least in Spain, every 10 years or
  so.} or the introduction of new degrees) crisis could be an opportunity to
introduce new technologies. The reason being that it does not bring major
changes in attitude. Although changes driven by external forces do offer the
chance of piloting new technologies, they do not seem to bring internal changes
in educators' attitudes (which, after all, is bound to be the same). In absence
of a clear answer in this direction, the right moment to introduce new
technologies is always when the IT and managing staff is ready to support it
(since, as we have seen before, ``official'' support is one of the factors that
is most valued by teachers).
